% @brief    LaTeX2e Resume for Vasil G. Slavov
\documentclass[margin,line]{resume}
\usepackage{hyperref}

%\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
%\def\CSharp{{\rm C\raise.5ex\hbox{\small \#}}}

\begin{document}
\name{\Large Vasil Slavov}
\address{
+1-816-255-0338 \ \ \ \ \ vgslavov@umkc.edu \ \ \ \ \ http://about.me/vgs
}
% http://v.web.umkc.edu/vsfgd
\begin{resume}

% Contact Information
%    \section{\mysidestyle Contact\\Information}
%
%    \hfill phone: +1-816-255-0338          \vspace{0mm}\\\vspace{0mm}%
%    \hfill e-mail: vgslavov@umkc.edu          \vspace{0mm}\\\vspace{0mm}%
%    \hfill web: v.web.umkc.edu/vsfgd
%\vspace{0mm}\\\vspace{-4.5mm}%

% Research Interests
    \section{\mysidestyle Research\\Interests}
    \begin{list3}
        \item Linked Data, Semantic Web, Big Data, NoSQL systems
        \item Scalable RDF query processing using a cloud infrastructure, RDF quadruples
        \item Federated SPARQL query processing
        \item Cardinality estimation of queries over semi-structured data using gossip-based algorithms
        \item RDF and XML data models in DHTs
    \end{list3}\vspace{-1.5mm}
   
% Education
    \section{\mysidestyle Education}

    \textbf{University of Missouri-Kansas City}, Kansas City, MO\\
    \textsl{Ph.D. Candidate in Computer Science}, GPA 3.95 \hfill \textbf{Spring 2011 -- December 2014}\vspace{-3mm}\\\vspace{-1mm}%
    \vspace{1mm}
    \begin{list3}
        %\item Dissertation topic: Cardinality Estimation of Basic Graph Patterns in Federated SPARQL Queries
        \item Dissertation topic: Fast Processing of SPARQL Queries on RDF Quadruples
        \item Advisor:  Professor Praveen Rao
    \end{list3}\vspace{-1.5mm}
    \textsl{M.S. in Computer Science}, GPA 3.95 \hfill \textbf{Spring 2008 -- Summer 2012}\vspace{-3mm}\\\vspace{-1mm}%
    \vspace{1mm}
    \begin{list3}
        \item Thesis topic: A Study of Gossip Algorithms for Internet-Scale Cardinality Estimation of Distributed XML Data
        \item Advisor:  Professor Praveen Rao
    \end{list3}\vspace{-1.5mm}
    \textbf{William Jewell College}, Liberty, MO\\
    \textsl{B.A. in Computer Science \& Math}, Summa Cum Laude, GPA 3.97 \hfill \textbf{Spring 2001 -- Spring 2005}\vspace{-3mm}\\\vspace{-1mm}%

% Honors and Awards
    \section{\mysidestyle Honors and\\Awards} 
    \begin{list3}
    %\item School of Graduate Studies Travel Grant, 2014, UMKC
    \item Outstanding Ph.D. Student in CS, 2012, School of Computing and Engineering, UMKC
    \item Balaji Krithikaivasan Memorial Student Travel Grant, CSEE, 2012, 2014, UMKC
    \item Dean's International Computing \& Engineering (DICE) award, SCE, UMKC
    \item Computer Science Faculty Award for the Outstanding Junior and Senior in CS, 2004, 2005, WJC
    \item Phi Epsilon Honor Society, 2005
    \item Who's Who Among Students in American Universities and Colleges, 2005
    %\item Certificate of Achievement, Undergraduate Colloquium 2004, WJC
    \item Kappa Mu Epsilon National Mathematics Honor Society, 2003
    \item Alpha Lambda Delta National Academic Honor Society for Freshmen, 2001
    \item Dean's List (7 semesters), WJC
    %\item Azima Scholarship
    \end{list3}

% Publications
    \section{\mysidestyle Publications}

\textbf{Vasil Slavov}, Anas Katib, Praveen Rao, Srivenu Paturi, Dinesh Barenkala.
    ``Fast Processing of SPARQL Queries on RDF Quadruples."
    To appear in \textsl{Proceedings of the 17th International Workshop on the Web and Databases} (\textbf{WebDB 2014}), Snowbird, UT, June 2014.
\url{http://v.web.umkc.edu/vsfgd/files/riq-webdb-paper.pdf}

\vspace{-2mm}
    \textbf{Vasil Slavov}, Anas Katib, and Praveen Rao.
    ``Tool for Internet-Scale Cardinality Estimation of XPath Queries over Distributed Semistructured Data."
    \textsl{Proceedings of the 30th IEEE International Conference on Data Engineering} (\textbf{ICDE 2014}), Chicago, IL, April 2014. (Demo)
\url{http://dx.doi.org/10.1109/ICDE.2014.6816758}

\vspace{-2mm}
    \textbf{Vasil Slavov} and Praveen Rao.
    ``A Gossip-Based Approach for Internet-Scale Cardinality Estimation of XPath Queries over Distributed Semistructured Data."
    \textsl{The International Journal on Very Large Databases} (\textbf{VLDB Journal 2014}), Volume 23, Issue 1, 2014, pp. 56--71. \url{http://dx.doi.org/10.1007/s00778-013-0314-1}
    
\vspace{-2mm}
    \textbf{Vasil Slavov}, Praveen Rao, Srivenu Paturi, Tivakar Swami, Michael Barnes, Deepthi Rao, and Raghuvarun Palvai.
    ``A New Tool for Sharing and Querying of Clinical Documents Modeled Using HL7 Version 3 Standard."
   \textsl{Computer Methods and Programs in Biomedicine, Elsevier} (\textbf{CMPB Journal 2013}), Volume 112, Issue 3, December 2013, pp. 529--552. \url{http://dx.doi.org/10.1016/j.cmpb.2013.07.002}

\vspace{-2mm}
    \textbf{Vasil Slavov}, Praveen Rao, Dinesh Barenkala, and Srivenu Paturi.
    ``Performance of RDF Query Processing on the Intel Single-chip Cloud Computer (SCC)."
    \textsl{Proceedings of the 6th Many-core Applications Research Community Symposium} (\textbf{MARC 2012}), Toulouse, France, July 2012, pp. 7--12. \url{http://hal.archives-ouvertes.fr/hal-00718955}
    
\vspace{-2mm}
    \textbf{Vasil Slavov} and Praveen Rao.
    ``Towards Internet-Scale Cardinality Estimation of XPath Queries over Distributed XML Data."
    \textsl{Proceedings of the 6th International Workshop on Networking Meets Databases} (\textbf{NetDB 2011}), Athens, Greece, June 2011, pp. 1--8. \url{http://research.microsoft.com/en-us/um/people/srikanth/netdb11/netdb11papers/netdb11-final1.pdf}

%\vspace{-2mm}
%    Dipali Pal, Praveen Rao and \textbf{Vasil Slavov}.
%    ``A New Signature Based Approach for Indexing and Querying of Graphs."
%    \textsl{The VLDB Journal}. \textbf{[under review]}

\newpage        
% Professional Experience
    \section{\mysidestyle Professional\\Experience}
    
    \begin{format}
    \title{l}\dates{r}\\
    \employer{l}\location{r}\\
    \end{format}

    \employer{\textsl{University of Missouri-Kansas City}}
    \title{\textbf{Graduate Research Assistant}}
    \location{Kansas City, MO}
    \dates{\textbf{September 2011 -- present}}
    \begin{position}\end{position}

    \employer{\textsl{Bloomberg L.P.}}
    \title{\textbf{R\&D Developer, Intern}}
    \location{New York, NY}
    \dates{\textbf{May 2014 -- August 2014}}
    \begin{position}
    \end{position}
    
    In R\&D Transactional Applications, Fixed Income Electronic Trading team
    \begin{list3}
    \item Developed a regression testing system for multiple large-scale transactional applications in C++ and JavaScript
    \end{list3}

    \employer{\textsl{Bloomberg L.P.}}
    \title{\textbf{R\&D Developer, Intern}}
    \location{New York, NY}
    \dates{\textbf{May 2013 -- August 2013}}
    \begin{position}

    In R\&D Transactional Applications, Fixed Income Electronic Trading team
    \begin{list3}
    \item Developed and evaluated log analytics solutions based on NoSQL systems
    \item Developed an automated testing system for transactional applications in Python
    \end{list3}
    \end{position}
    
    \employer{\textsl{Kansas City Art Institute}}
    \title{\textbf{Network Systems Analyst}}
    %\title{\textbf{Network and System Administrator}}
    \location{Kansas City, MO}
    \dates{\textbf{July 2006 -- August 2011}}
    \begin{position}
    \vspace{-2mm}
    %\begin{list3}
    %\item Responsible for all servers and network equipment
    %\item Migrated all network equipment from Cisco to 3Com
    %\item Migrated from Microsoft Exchange to Google Apps
    %\item Set up and maintained: NAS, VoIP, Wireless, Backup, Virtualization, QoS, Security
    %\end{list3}
    \end{position}

    \employer{\textsl{William Jewell College}}
    \title{\textbf{Open Systems Analyst}}
    %    \title{\textbf{Open Systems Analyst and Academic Technologist}}
    \location{Liberty, MO}

    \dates{\textbf{June 2005 -- July 2006}}
    \begin{position}
    \vspace{-2mm}
%    \begin{list2}
%    \item Set up and maintained all campus firewalls using the OpenBSD Packet Filter (PF)
%    \item Set up and maintained all campus computer labs
%    \end{list2}
    \end{position}

% Technical Skills
    \section{\mysidestyle Languages and Technologies} 

    \textbf{Languages}: C++, Python, C, shell, JavaScript, regex, SPARQL, ANTLR, C\#, MPI, \LaTeXe\\
    \textbf{Cloud Platforms/Distributed Networks}: Amazon Elastic Compute Cloud (EC2), IBM SmartCloud Enterprise, PlanetLab\\
    \textbf{Frameworks/Engines}: ElasticSearch, Hadoop, AngularJS, Distributed Hash Tables (Chord)\\
    \textbf{Tools}: git, gdb, Valgrind, CVS\\
    \textbf{Operating Systems}: {\sc UNIX}/Linux, Mac OS X Server, Windows Server
    
% Projects
    \section{\mysidestyle Technical Experience}
    \textbf{Regression testing system} (2014). \textsl{C++, JavaScript}. Developed a regression testing system for multiple large-scale transactional applications.
    %\textbf{DVR} (2014). \textsl{C++, BAS, DMP Subscriber API, Rapid, MD5}. Developed a generic regression testing system for replaying a large number of transactions and comparing their outputs using different hashing methods.

    \vspace{-2mm}
    \textbf{RIQ: RDF Indexing on Quadruples} (2013 -- 2014). \textsl{C++, Dablooms, Raptor2, LSH}. Implemented and evaluated a decrease-and-conquer strategy for fast processing of SPARQL queries on very large RDF quadruple datasets  (over a billion quads) using Counting Bloom Filters and Locality Sensitive Hashing.
    
    \vspace{-2mm}
    \textbf{Automated testing system} (2013). \textsl{Python}. Developed an automated testing suite for replaying production trades of transactional applications.
    
   \vspace{-2mm}
    \textbf{Log analytics} (2013). \textsl{AngularJS, ElasticSearch, Kibana, Logstash}. Evaluated log analytics solutions and developed a transaction (Splunk-like) module for Kibana in AngularJS.

    \vspace{-2mm}    
    \textbf{XGossip} (2010 -- 2013). \textsl{C++, Sfslite, LSH, Chord DHT, Amazon EC2}. Implemented and evaluated a novel gossip algorithm for estimating the number of XML documents that contain a match for an XPath query in a large-scale network in the presence of churn and failures.

\vspace{-2mm}
    \textbf{RDF query processing on Intel SCC} (2011). \textsl{MPICH, C}. Evaluated large-scale RDF query processing on the 48-core Intel Single-chip Cloud Computer (SCC) using task and data parallelism.
    
\vspace{-2mm}
    \textbf{SyncMe!} (2010). \textsl{C\#, .NET, Facebook Graph API, Twitter REST API, Google Calendar API, Google OAuth}. In a team, designed and developed a web site for aggregating Twitter and Facebook events on a user's Google Calendar.

%\vspace{-2mm}
 %   \textbf{Link-state protocol} (2009). \textsl{C, Linux}. Implemented an OSPF-like link-state routing protocol on top of UDP.

%\vspace{-2mm}
%    \textbf{Intelligent file transfer protocol} (2009). \textsl{C, Zlib, TCP, Linux}. Designed and developed an intelligent, BitTorrent-like file transfer protocol.

%\vspace{-2mm}
%    \textbf{P2P file system} (2008). \textsl{C++, Chord DHT, Linux, PlanetLab}. Designed, implemented, and evaluated a distributed file system using the Chord DHT framework.

%\vspace{-2mm}
 %   \textbf{Web server} (2008). \textsl{C, TCP, Linux}. Designed and implemented a lightweight web server.
    
%\vspace{-2mm}
 %   \textbf{Comparison of the Performance Characteristics of the OpenBSD Stateful Packet Filter (PF) and Microsoft Internet Security and %Acceleration (ISA) Server} (2004). Undergraduate Colloquium, William Jewell College.

%\vspace{-2mm}    
 %   \textbf{Velositor} (2004). \textsl{Python, Apache, Cerner Millennium API}. In a team, designed, developed, and presented a web-based mobile application, which fetches patient data from Cerner Corp. Millennium database and displays it for use by physicians.

%\vspace{-2mm}
 %  \textbf{Sentinel} (2003). \textsl{C, Linux}. Designed and developed a magnetic card reader client-server application for the Computer Science Lab, William Jewell College.

\newpage
% Talks
    \section{\mysidestyle Talks}
    \begin{list2}
    \item Presentations
    \begin{list3}
    \item Fast Processing of SPARQL Queries on RDF Quadruples. The 17th International Workshop on the Web and Databases (WebDB), Snowbird, UT, June 22, 2014.
    \item Tool for Internet-Scale Cardinality Estimation of XPath Queries over Distributed Semistructured Data. The 30th IEEE International Conference on Data Engineering (ICDE), Chicago, IL, April 3, 2014.
    \item Performance of RDF Query Processing on the Intel SCC. The 6th Many-core Applications Research Community (MARC) Symposium, Toulouse, France, July 19, 2012.
    \item Internet-Scale Cardinality Estimation of XPath Queries over Distributed XML Data. UMKC CSEE Seminar Series, April 2, 2012.
    \end{list3}
    \item Guest Lectures
    \begin{list3}
    \item Principles of Big Data Management course, UMKC, Fall 2014
    \item Data Structures course, UMKC, Fall 2013
    \item Introduction to Database Management Systems course, UMKC, Spring 2013 and Fall 2013
    \item Advanced Operating Systems course, UMKC, Fall 2010, 2011, and 2013
    \end{list3}
    \end{list2}

% Service
    \section{\mysidestyle Service}
    \begin{list2}
    \item Reviewer
    \begin{list3}
    \item Journal of Parallel and Distributed Computing, Elsevier (JPDC), 2014
    \item International Journal of Distributed Sensor Networks (IJDSN), 2014
    \end{list3}
    \item External reviewer
    \begin{list3}
    \item International Conference on Database and Expert Systems Applications (DEXA), 2011 - 2014
    \end{list3}
    \item Organizer for School of Computing and Engineering E-Week Quiz Contest, UMKC, 2012
    \end{list2}
 
\end{resume}
\end{document}
